Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Strip some of doctest's output
Step 1 -> Start with a trivial example
Add a comment

\subsubsection{Step 1}

@@

\begin{quote}
\small
\begin{verbatim}
$ doctest Fib.hs
There is one test, with one single interaction.
Examples: 1  Tried: 1  Errors: 0  Failures: 0
\end{verbatim}
\end{quote}

@@

>>>>

\subsubsection{Start with a minimal implementation}

@@

\begin{quote}
\small
\begin{verbatim}
$ doctest Fib.hs
Examples: 1  Tried: 1  Errors: 0  Failures: 0
\end{verbatim}
\end{quote}

@@

\begin{quote}
    TBD: do we want to add something like this?

    At this stage we do not care about invalid input or performance.
    We are happy with an implementation that works for small
    non-negative numbers.
\end{quote}
